ms_figures

### 2018-02-12 man/ms_figures.Rmd
include suggestions by GGI

**Figure 1**. Distribution of *Quercus pyrenaica* forests in Iberian Peninsula (a) and in Sierra Nevada mountain range, where three cluster of oak populations have been identified [@PerezLuque2015] (showed in different colour) (b). A grid of with the MODIS pixels for each population is shown (see material and methods). Detailed location of the sampling sites: northern (San Juan, SJ) (c) and southern ones (Cáñar: CALow and CAHigh)(d). Colour Orthophotography of 2009 from Regional Ministry of the Environment, Regional Government of Andalusia.

@@

**Figure 2.** Comparison of EVI profile for the reference period (*gray*) and during the 2005 (*green*) and 2012 (*blue*) drought events (a). EVI standardized anomaly ($EVI~sa$) during the period 2000-2016 for northern and southern populations (b). Error bars show standard error.

@@

**Figure 3.** Response of northern (*black*) and southern (*blue*) populations of *Q. pyrenaica* forests to drought in terms of resistance, recovery and resilience of greenness (EVI; a) and tree growth (BAI; b) for the years 2005 and 2012. Different letters above bars indicate significant post hoc differences between groups (see material and methods).

@@

**Figure 4.** Response of *Q. pyrenaica* forests to 2005 (*black*) and 2012 (*red*) drought events in terms of resistance, recovery and resilience of greenness (EVI; a) and tree growth (BAI; b) by site. Different letters above bars indicate significant post hoc differences between groups (see material and methods).

@@

pgc_median <- gc_treesMed %>% ggplot() +
  geom_bar(aes(x=year, y=per_pos), fill=colorpositivo, colour=colorpositivo, stat = "identity", position = "dodge") + 
  geom_bar(aes(x=year, y=(-1)*per_neg), fill=colornegativo, colour=colornegativo, stat = "identity", position = "dodge") +
  facet_wrap(~site_sorted, nrow = 3, labeller = as_labeller(label_site)) + 
  scale_y_continuous(sec.axis = sec_axis(~ ., name = '# trees', breaks = c(0,15,30))) +
  geom_line(aes(x=year, y=total_tree), colour = 'black') + 
  theme_bw() + ylab('% trees') +
  geom_hline(yintercept=c(50, -50), linetype=2, alpha=.4) +
  theme(panel.grid.minor = element_blank(), 
        strip.background = element_rect(colour='black', 
                                        fill='white')) 
pgc_median

@@

**Figure 9**. Percentage of *Q. pyrenaica* trees affected by GC > 25 % by site. *Black* line shows number of trees (rigth-axis).

>>>>

**Figure 1**. Distribution of *Quercus pyrenaica* forests in Iberian Peninsula (a) and in Sierra Nevada mountain range, where three clusters of oak populations have been identified [@PerezLuque2015] (showed in different colour) (b). A grid of with the MODIS pixels for each population is shown (see material and methods). Detailed location of the sampling sites: northern (San Juan, SJ) (c) and southern ones (Cáñar: CALow and CAHigh) (d). Colour Orthophotography of 2009 from Regional Ministry of the Environment, Regional Government of Andalusia.

@@

**Figure 2.** Comparison of EVI profile for the reference period (*gray*) and during the 2005 (*green*) and 2012 (*blue*) drought events (a) (mean of all analyzed pixels). EVI standardized anomaly ($EVI~sa$) during the period 2000-2016 for northern and southern populations (b). Error bars show standard error.

@@

**Figure 3.** Response of northern (*black*) and southern (*blue*) populations of *Q. pyrenaica* forests to drought in terms of resistance, recovery and resilience of greenness (EVI; a) and tree radial growth (BAI; b) for the years 2005 and 2012. Different letters above bars indicate significant post hoc differences between groups (see material and methods).

@@

**Figure 4.** Response of *Q. pyrenaica* forests to 2005 (*black*) and 2012 (*red*) drought events in terms of resistance, recovery and resilience of greenness (EVI; a) and tree radial growth (BAI; b) by site. Different letters above bars indicate significant post hoc differences between groups (see material and methods).

@@

pgc_median50 <- gc_treesMed50 %>% ggplot() +
  geom_bar(aes(x=year, y=per_pos), fill=colorpositivo, colour=colorpositivo, stat = "identity", position = "dodge") + 
  geom_bar(aes(x=year, y=(-1)*per_neg), fill=colornegativo, colour=colornegativo, stat = "identity", position = "dodge") +
  facet_wrap(~site_sorted, nrow = 3, labeller = as_labeller(label_site)) + 
  scale_y_continuous(sec.axis = sec_axis(~ ., name = '# trees', breaks = c(0,15,30))) +
  geom_line(aes(x=year, y=total_tree), colour = 'black') + 
  theme_bw() + ylab('% trees') +
  geom_hline(yintercept=c(50, -50), linetype=2, alpha=.4) +
  theme(panel.grid.minor = element_blank(), 
        strip.background = element_rect(colour='black', 
                                        fill='white')) 
pgc_median50

@@

**Figure 9**. Percentage of *Q. pyrenaica* trees affected by GC > 50 % by site. *Black* line shows number of trees (rigth-axis).
